Emittance preservation of an electron bunch in a loaded quasi-linear plasma wakefield

### 2017-08-01 Tex/Paper.tex
Added emittance figures

Earlier simulations with witness beam $\sigma_{r} = 100\unit{\mu m}$ caused the beam radius to undergo rapid transverse
evolution as the beam enters the plasma, reducing its $\sigma_{r}$ from $100\unit{\mu m}$ to $< 10\unit{\mu m}$
\cite{berglyd_olsen:2016}. This is due to a mismatch between beam emittance and the plasma density. This relation is
given by
\begin{align}
    \beta = \frac{\sigma_r^2}{\epsilon_g} = \frac{\lambda_p}{2\pi}\sqrt{2\gamma_{rel}}, \label{EQ:Matched}
\end{align}
where $\lambda_{p}$ is the plasma wavelength. In these simulations we have used matched beams for emittances between
$2$ and $6\unit{\mu m}$, corresponding to $\sigma_{r}$ ranging from $5.25\unit{\mu m}$ to $9.09\unit{\mu m}$.

@@

For Gaussian beams a reasonable flat field and consequently low energy spread can be achieved by controlling the charge
density. In our case, with a matched beam to the plasma density \ref{EQ:Matched}, we are limited on how much total
charge we can accelerate. The test case shown in figures \ref{Fig:BeamLoading} and \ref{Fig:PlasmaDenTWake} has a total
charge of $100\unit{pC}$ with a $\sigma_{r}=5.23\unit{\mu m}$ matching an initial normalised emittance
$\epsilon_{0} = 2\unit{\mu m}$.

@@

@@

@@

% ******************************************************************************************************************** %
\section[\label{S:D}]{Discussion}
% ******************************************************************************************************************** %

% ******************************************************************************************************************** %
\section[\label{S:C}]{Conclusion}
% discussion of optimal electron beam parameters
% implications for AWAKE Run 2
% ******************************************************************************************************************** %

@@

The simulations forming the basis for this study have been made possible using the open source version of QuickPIC
released in early 2017 and owned by UCLA.

These numerical simulations have been made possible through access to the Abel computing cluster in Oslo, Norway
maintained by UNINETT Sigma2 AS and financed by the Research Council of Norway, the University of Bergen, the University
of Oslo, the University of Tromsø and the Norwegian University of Science and Technology. Project code: nn9303k.

>>>>

Earlier simulations with witness beam $\sigma_{r} = 100\unit{\mu m}$ caused the beam radius to undergo rapid transverse
evolution as the beam enters the plasma, reducing its $\sigma_{r}$ from $100\unit{\mu m}$ to $< 10\unit{\mu m}$
\cite{berglyd_olsen:2016}. This is due to a mismatch between beam emittance and the plasma density. This relation is
given by
\begin{align}
    \beta = \frac{\sigma_r^2}{\epsilon_g} = \frac{\lambda_pe}{2\pi}\sqrt{2\gamma_{rel}}, \label{EQ:Matched}
\end{align}
where $\lambda_{p}$ is the plasma wavelength. In these simulations we have used matched beams for emittances between
$2$ and $6\unit{\mu m}$, corresponding to $\sigma_{r}$ ranging from $5.25\unit{\mu m}$ to $9.09\unit{\mu m}$.

@@

@@

For Gaussian beams a reasonable flat field and consequently low energy spread can be achieved by controlling the charge
density. In our case, with a matched beam to the plasma density defined by equation \ref{EQ:Matched}, we are limited on
how much total charge we can accelerate. The test case shown in figures \ref{Fig:BeamLoading} and
\ref{Fig:PlasmaDenTWake} has a total charge of $100\unit{pC}$ with a $\sigma_{r}=5.23\unit{\mu m}$ matching an initial
normalised emittance $\epsilon_{0} = 2\unit{\mu m}$.

@@

\begin{figure*}[hbt]
    \includegraphics[width=0.495\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamEmittance}
    \includegraphics[width=0.495\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamEmittanceOffset}
    \caption{\label{Fig:BeamEmitt} The red lines show a moving window calculation of transverse normalised emittance for
        an on-axis beam with respect to the drive beam axis (left) and an offset beam (right) with an offset of one
        $\sigma_{x}$ in the x plane. The moving window for emittance calculation is longitudinal slices of
        $l = 4\times\Delta\xi = 18.75\unit{\mu m}$ with a $\Delta\xi$ resolution. Only slices with more than $100$ macro
        particles have been included, which accounts for the abrupt edge as well as the noise at either end of the beam
        due to low statistics. The blue lines show the peak electron beam density profile. For reference, the plasma 
        density profile is included in green, but scaled up by a factor of $100$ to be visible. The solid lines are at
        the plasma entry point, the dashed lines after $4\unit{m}$ of plasma, the dash-dotted after $40\unit{m}$, and
        the dotted after $100\unit{m}$. In order to sustain a stable accelerating field for the witness beam, these
        simulations were run with an LHC energy drive beam of $7\unit{TeV}$ to avoid dephasing which causes the
        structure to brake down after about $50\unit{m}$.}
\end{figure*}

The witness beam's self-generated bubble prevents the tailing end of the beam to see any measurable emittance growth.
For the majority of the cases we studied that maintained a stable accelerating structure, about $70\%$ of the beam
retained its initial emittance. Figure \ref{Fig:BeamEmitt} shows the $100\unit{pC}$ and $\sigma_{z} = 60\unit{\mu m}$
case extended to a $100\unit{m}$ plasma case and the drive beam energy increased to $7\unit{TeV}$ (LHC energy) to
prevent dephasing, which for the SPS beam case starts to become significant after about $50\unit{m}$.

The on-axis density of the electron beam increases as its gamma factor increases and its transverse size decreases. The
beam radius follows the matched beam equation \ref{EQ:Matched} with $\lambda_{pe} = \lambda_{0}$.

@@

% ******************************************************************************************************************** %
\section[\label{S:D}]{Discussion}
% discussion of optimal electron beam parameters
% implications for AWAKE Run 2
% ******************************************************************************************************************** %

% ******************************************************************************************************************** %
\section[\label{S:C}]{Conclusion}
% ******************************************************************************************************************** %

@@

The simulations for this study have been run using the open source version of QuickPIC released in early 2017 and owned
by UCLA.

These numerical simulations have been made possible through access to the Abel computing cluster in Oslo, Norway. Abel
is maintained by UNINETT Sigma2 AS and financed by the Research Council of Norway, the University of Bergen, the
University of Oslo, the University of Tromsø and the Norwegian University of Science and Technology. Project code for
this work is nn9303k.
